Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-12-01 paper/responseToReviewers.tex

\usepackage{color}
\newcommand{\gl}[1]{\textcolor{red}{Gregoire : #1}}
\newcommand{\eb}[1]{\textcolor{magenta}{Emmanouil : #1}}
\newcommand{\ml}[1]{\textcolor{blue}{ Mathieu : #1}}

\begin{document}

\maketitle

We would like to thank the editor and the reviewers for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of the reviewer's comments, with references to the revised manuscript where appropriate.

@@

\item \emph{line 60: auditory and modulation filter – nonsense.}

\item \emph{"unsupervised classification" it is clustering then.}

\item \emph{"time-frequency perspective or a machine learning perspective" is it imposed versus learned representation? }

\item \emph{Equations 9 and 10 are superfluous.}
These equations were removed from the paper.

### 2016-12-01 paper/structureScene.tex
R1-21: Equations 9 and 10 are superfluous

To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we apply the affine transformation
\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mu[ \mathbf{S}\boldsymbol{X}](\gamma)}{\sigma[ \mathbf{S}\boldsymbol{X}](\gamma)}
\end{equation}
where $\mu[ \mathbf{S}\boldsymbol{X}](\gamma) = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the sample mean of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma[\mathbf{S}\boldsymbol{X}] (\gamma) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mu[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
is the sample standard deviation.

The vectors $\mu[\mathbf{S}\boldsymbol{X}(\gamma)]$ and $\sigma[\mathbf{S}\boldsymbol{X}](\gamma)$ are estimated from the training set only, and the same affine transformation is subsequently applied to all samples in the training set and the test set.

>>>>

To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we substract the sample means $\mu[\mathbf{S}\boldsymbol{X}(\gamma)]$ to $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and divide the result by the sample standard deviations $\sigma[\mathbf{S}\boldsymbol{X}] (\gamma)$.
The vectors $\mu[\mathbf{S}\boldsymbol{X}(\gamma)]$ and $\sigma[\mathbf{S}\boldsymbol{X}](\gamma)$ are estimated from the training set only, and the same affine transformation is subsequently applied to all samples in the training set and the test set.
